---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/poissonconsulting/subfoldr2.svg?branch=master)](https://travis-ci.org/poissonconsulting/subfoldr2)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/subfoldr2?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/subfoldr2)
[![Coverage status](https://codecov.io/gh/poissonconsulting/subfoldr2/branch/master/graph/badge.svg)](https://codecov.io/github/poissonconsulting/subfoldr2?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)

# subfoldr2

`subfoldr2` is an opinionated R package to facilitate the saving and loading of 
R objects, data frames, strings, numbers and plots.

## Main Directory

By default files are saved to `output` unless overridden using `sbf_set_main()`.

## Saving and Loading R Objects

An R object can be written using `sbf_save_object()` and read using `sbf_load_object()`.
All R objects are saved as `.rds` files in `objects` (in the main folder).
The user can save objects to a particular directory within `objects` using `sbf_set_sub()`
or the `sub = sbf_get_sub()` argument of `sbf_save_object()`.
This is useful if the user wishes to save groups of objects together.
```{r}
library(subfoldr2)
sbf_set_main(tempdir())

x <- 1
sbf_save_object(x)
sbf_save_object(3, "y")
x <- x * 2
sbf_set_sub("twice")
sbf_save_object(x)

list.files(sbf_get_main(), recursive = TRUE)
sbf_reset_sub()
sbf_load_object("x")
sbf_load_object("x", sub = "twice")
```
The user can load all the objects in the current sub folder into the calling environment 
using `sbf_load_objects()` or recursively load all the objects as a list column in a data frame
using `sbf_load_objects_recursive()`.
```{r}
rm(x)
sbf_load_objects()
print(x)
sbf_load_objects_recursive()
```
To recursively delete a subdirectory call `sbf_set_sub()` with `rm = TRUE`.
```{r}
sbf_set_sub("twice", rm = TRUE, ask = FALSE)
sbf_load_objects_recursive()
```
All the objects in the calling environment can be saved to the current subdirectory using `sbf_save_objects()`.
```{r}
ls()
sbf_save_objects()
sbf_load_objects_recursive()
```


## Saving and Loading Data Frames, Numbers and Strings

There are equivalent.


## Installation

To install the latest development version from the Poisson drat [repository](https://github.com/poissonconsulting/drat)
``` r
install.packages("drat")
drat::addRepo("poissonconsulting")
install.packages("subfoldr2")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/subfoldr2/issues).

[Pull requests](https://github.com/poissonconsulting/subfoldr2/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.